


\refstepcounter{section}\section*{\thesection\quad  How important is the problem to practice?}
	
\refstepcounter{section}\section*{\thesection\quad  How will you know if the solution/s that you will achieve would be better than existing ones?}	

\refstepcounter{subsection}\subsection*{\thesubsection\quad How will you measure the improvement/s?}	

\refstepcounter{subsubsection}\subsubsection*{\thesubsubsection\quad  What is/are your basis/bases for the improvement/s?}

\refstepcounter{subsubsection}\subsubsection*{\thesubsubsection\quad  Why did you choose that/those basis/bases?}
		
\refstepcounter{subsubsection}\subsubsection*{\thesubsubsection\quad  How significant are your measure/s of the improvement/s?}

\refstepcounter{section}\section*{\thesection\quad What is the difference of the solution/s from existing ones?}
	
\refstepcounter{subsection}\subsection*{\thesubsection\quad How is it different from previous and existing ones?}

\refstepcounter{section}\section*{\thesection\quad What are the assumptions made (that are behind for your proposed solution to work)?}
	
\refstepcounter{subsection}\subsection*{\thesubsection\quad Will your proposed solution/s be sensitive to these assumptions?}
	
\refstepcounter{subsection}\subsection*{\thesubsection\quad Can your proposed solution/s be applied to more general cases when some assumptions are eliminated? If so, how?}

\refstepcounter{section}\section*{\thesection\quad What is the necessity of your approach / proposed solution/s?}

\refstepcounter{subsection}\subsection*{\thesubsection\quad What will be the limits of applicability of your proposed~solution/s?}
				
\refstepcounter{subsection}\subsection*{\thesubsection\quad What will be the message of the proposed solution to technical people?  How about to non-technical managers and busines people?}
	
\refstepcounter{section}\section*{\thesection\quad How will you know if your proposed solution/s is/are correct?}
	
\refstepcounter{subsection}\subsection*{\thesubsection\quad Will your results warrant the level of mathematics used (i.e., will the end justify the means)?}
	   
\refstepcounter{section}\section*{\thesection\quad Is/are there an/\_ alternative way/s to get to the same solution/s?}

\refstepcounter{subsection}\subsection*{\thesubsection\quad Can you come up with illustrating examples, or even better, counterexamples to your proposed solution/s?}

\refstepcounter{subsection}\subsection*{\thesubsection\quad Is there an approximation that can arrive at essentially the same proposed solution/s more easily?}
	
\refstepcounter{section}\section*{\thesection\quad If you were the examiner of your \documentType, how would you present the \documentType \ in another way?  Give your remarks, especially for your methodology and the results and discussions.}

% \MakeTextLowercase{\documentType} currently fails inside section{}
	
\refstepcounter{subsection}\subsection*{\thesubsection\quad What are the weaknesses of your \documentType, specifically  your methodology and the results and discussions?}
