
\section{Standards}

\begin{itemize}
    \item \textbf{Software:}
    \begin{itemize}
        \item ISO/IEC 25024 – Data Quality
        \item ISO/IEC 23053 – Machine Learning
        \begin{itemize}
            \item Ensures a standard that provides a framework for AI and ML system lifecycle processes.
            \item Ensures high-quality training data and fair sorting results.
            \item Helps define performance metrics to assess the efficiency of the sorting process.
        \end{itemize}
    \end{itemize}
    
    \item \textbf{Hardware:}
    \begin{itemize}
        \item \textbf{Rotating Conveyor Table}
        \begin{itemize}
            \item ISO 12100:2010 – Safety of Machinery
            \begin{itemize}
                \item Ensures risk assessment and risk reduction in machine design.
                \item Prevents hazards like pinch points, dust exposure, and mechanical failures.
            \end{itemize}
        \end{itemize}
        
        \item \textbf{Motor}
        \begin{itemize}
            \item IEC 61800-5-1 – Electrical Safety of Drive Systems
            \begin{itemize}
                \item Ensures motor drivers and stepper controllers provide safe and regulated power to motors.
            \end{itemize}
        \end{itemize}
        
        \item \textbf{Precision Scale}
        \begin{itemize}
            \item EIA/TIA-232 (RS-232) – Standard for Serial Communication
            \begin{itemize}
                \item Defines baud rates, data bits, stop bits, and parity settings for UART communication.
                \item Useful for setting consistent serial communication parameters between Arduino and Python.
            \end{itemize}
        \end{itemize}
        
        \item \textbf{Lighting}
        \begin{itemize}
            \item ISO 3664:2009 – Standardized Lighting Conditions for Color Evaluation
            \begin{itemize}
                \item Defines proper lighting conditions for inspecting color variations in coffee beans.
                \item Essential for ensuring consistent color detection under different environmental conditions.
            \end{itemize}
        \end{itemize}
    \end{itemize}
    
    \item \textbf{Coffee Beans / Datasets:}
    \begin{itemize}
        \item ISO/IEC 25024 – Data Quality for Machine Learning
        \begin{itemize}
            \item Ensures that computer vision models use high-quality, consistent datasets.
            \item Helps prevent errors in defect classification due to poor data labeling.
        \end{itemize}
        \item SCAA Standards for Coffee Bean Sorting
    \end{itemize}
\end{itemize}

\section{Summary}

Provide the gist of this chapter such that it reflects the contents and message.